Figures

### 2020-01-31 figures/00_maps.Rmd
add map of bathymetry locations, closes #21

>>>>

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
bathy_pnts <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE)
max_depth <- dt$lake_maxdepth_m
dt <- dt %>%
  mutate(lake_maxdepth_m = round(lake_maxdepth_m, 2)) %>%
  mutate(maxdepth_class = 
           smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, max(max_depth)), 
                     brackets = NULL, sep = " - ")
         ) %>% # unique(dt$maxdepth_class)
  dplyr::filter(!is.na(maxdepth_class))

dt_bathy <- st_drop_geometry(bathy_pnts) %>% 
  left_join(
    dplyr::distinct(dplyr::mutate(dplyr::select(dt, lagoslakeid, maxdepth_class, 
                                                has_limno, lake_waterarea_ha),
                  lagoslakeid = as.character(lagoslakeid)), lagoslakeid, .keep_all = TRUE),
            by = c("llid" = "lagoslakeid"))

dt_bathy <- st_sf(dt_bathy, geometry = dt_bathy$geom)

gg_bathy <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt_bathy, aes(color = maxdepth_class), 
                    size = 0.3, alpha = 1) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

gg_bathy
```

### 2020-01-31 manuscript/figures.Rmd
add map of bathymetry locations, closes #21

@@

```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=6.5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Summary of lake depth predictor variables.")
```

>>>>

![Summary of lake depth predictor variables.](../tables/01_predictors.pdf){width=65%}

```{r maps_dot_bathy, fig.cap = "Map of lake maximum depth measurements derived from lake bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```

@@
